Breeding bird indicators

### 2023-10-19 slitasje.Rmd
Specify that indicators are unique also to each ecosystem #83
New table. Fig for report.

Norwegian indicator name: Slitasje

```{r setup, include=FALSE}
library(knitr)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(tidyverse)
library(tibble)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT)
knitr::kable(metaData)
```

@@

### Temporal coverage

@@

#### Looking at the HIA

>>>>

Norwegian indicator name: **Slitasje**

```{r setup, include=FALSE}
library(knitr)
library(sf)
library(tmap)
library(ggpubr)
library(DT)
library(units)
library(eaTools)
library(tidyverse)
library(tibble)
library(flextable)
knitr::opts_chunk$set(echo = TRUE)

@@

```{r, echo=F}
metaData <- data.frame(Ecosystem,
                       "Økologisk egenskap" = Egenskap,
                       "ECT class" = ECT,
                       check.names = F)
flextable(metaData) %>%
  bg(bg = "lightblue", part="header") %>%
  theme_vanilla() %>%
  set_table_properties(layout = "autofit")
```

@@

### Temporal coverage {#temoporal-sli}

@@

```{r, include=FALSE, eval=FALSE}
# Figure for the report 2023

corrCheck %>%
  filter(hovedøkosystem == "naturligÅpneOmråderILavlandet") %>%
ggplot(aes(x = factor(infrastructureIndex), fill = factor(round(i_2020,2))))+
  geom_bar(position="fill")+
  theme_bw(base_size = 12)+
  guides(fill = guide_legend("Skalerte indikatorverdier"))+
  ylab("Andel av datapunkter")+
  xlab("Infrastrukturindeksen (kategorisk versjon)")+
  scale_fill_brewer(palette = "RdYlGn")
```
#### Looking at the HIA
